\chapter*{\Large Bibliografía}
%---Para incorporar al Indice de Contenidos
\addcontentsline{toc}{chapter}{\large Bibliografía}


\pagestyle{fancy}
\renewcommand{\sectionmark}[1]{\markright{#1}}

\lhead{}
\chead{}
\rhead{\Bibliografía}
\lfoot{}
\cfoot{}
\rfoot{\thepage}
\renewcommand{\headrulewidth}{0.4pt}
% \vspace{-1cm}

%  \def\bibname{\large Bibliograf{\'i}a}
% \begin{thebibliography}{60}
\begin{itemize}
\item Alani, H., Kim, S., Millard, D. E., Weal, M. J., Hall, W., Lewis, P. H., \& Shadbolt, N. R. (2003). Automatic ontology-based knowledge extraction from Web documents. IEEE Intelligent Systems, 18(1), 14–21. https://doi.org/10.1109/MIS.2003.1179189

\item Bernstein, A., Hendler, J., \& Noy, N. (2016). A new look at the semantic web. Communications of the ACM, 59(9), 35–37. https://doi.org/10.1145/2890489

\item Botoeva, E., Calvanese, D., Cogrel, B., Rezk, M., \& Xiao, G. (2016). OBDA beyond relational DBs: A study for MongoDB. In CEUR Workshop Proceedings (Vol. 1577).

\item Fernández-López, M. (1999). Overview Of Methodologies For Building Ontologies. In V. R. Benjamins, B. Chandrasekaran, A. Gómez-Pérez, N. Guarino, \& M. Uschold (Eds.), Proceedings of the IJCAI-99 workshop on Ontologies and Problem-Solving Methods (KRR5) (Vol. 18, pp. 1–13). Estocolmo, Suecia: CEUR-WS.

\item Fernández-Peña, F., Acosta-Sánchez, R., \& Ponce-Toste, Y. (2015). ViewOnto: modelo conceptual para la generación automática de vistas de datos. Ciencias de La Información, 46(1), 19–25.

\item Hevner, A. R., March, S. T., Park, J., \& Ram, S. (2004). Design Science in Information Systems Research. MIS Quarterly, 28(1), 75–105.

\item Jannach, D., Shchekotykhin, K., \& Friedrich, G. (2009). Automated ontology instantiation from tabular web sources—The AllRight system. Web Semantics: Science, Services and Agents on the World Wide Web, 7(3), 136–153. https://doi.org/https://doi.org/10.1016/j.websem.2009.04.002

\item Kharlamov, E., Brandt, S., Jimenez-Ruiz, E., Kotidis, Y., Lamparter, S., Mailis, T., … Moeller, R. (2016). Ontology-Based Integration of Streaming and Static Relational Data with Optique. In Proceedings of the 2016 International Conference on Management of Data (pp. 2109–2112). New York, NY, USA: ACM. https://doi.org/10.1145/2882903.2899385

\item Kharlamov, E., Hovland, D., Skjæveland, M. G., Bilidas, D., Jiménez-Ruiz, E., Xiao, G., … Waaler, A. (2017). Ontology Based Data Access in Statoil. Web Semantics: Science, Services and Agents on the World Wide Web, 44, 3–36. https://doi.org/https://doi.org/10.1016/j.websem.2017.05.005

\item Runeson, P., Host, M., Rainer, A., \& Regnell, B. (2012). Case Study Research in Software Engineering. John Wiley \& Sons, Inc (1st ed.). Wiley Publishing. https://doi.org/10.1002/9781118181034

\end{itemize}


